Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-11-05 Talk/Presentation.tex
Added trapezoidal shape, fuzzy algorithm, and things about features and rules to my presentation.
Added a few slides on KDD99.

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc} 
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.
\usepackage{amsmath}

@@

\subsection{Data Sets}
\begin{frame}
  \frametitle{title}

@@

\begin{frame}
	\frametitle{Encoding of features and rules}

>>>>

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc} 
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.
\usepackage{amsmath}
\usepackage{algorithmic}

@@

\subsection{Data Sets - KDD99 and RLD09}
\begin{frame}
  \frametitle{KDD99}
	\begin{itemize}
		\item Generated by simulating a military network environment in 1999.
		\item Has long been a standard data set for intrusion detection.
		\item Data in the set is classified as normal or attack activity.

		\item KDD99 uses 41 features.
		\begin{itemize}
		  	\item \emph{Features} are properties of a \emph{record}, (either an attack or normal activity), that are used to describe the activity.
		\end{itemize}

	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Some features of KDD99}
	\begin{enumerate}
		\item duration: length of the normal or attack activity
in seconds.
		\item src\_bytes: number of bytes sent from source to destination.
		\item num\_failed\_logins: number of failed login attempts.
		\item root\_shell: returns 1 if root shell is obtained, else returns 0.
		\item num\_access\_files: number of operations on access control files.
		\item srv\_count: number of connections to the same service as the current connection in the past two seconds.
		\item serror\_rate: percentage of connections that have ``SYN" errors.
		\item same\_srv\_rate: percentage of connections to the same service.
	\end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{RLD09}

@@

  \begin{columns}
  \begin{column}{0.4\textwidth}
  \begin{itemize}
  	\item Trapezoidal shape
  \end{itemize}

  \includegraphics[width=0.95\textwidth]{../trapFigure.jpg}

  \begin{itemize}
	\item The parameters are the values of a feature.
  \end{itemize}

  \end{column}

  \begin{column}{0.6\textwidth}
  \begin{itemize}
  	\item Fuzzy algorithm
  \end{itemize}

\begin{algorithmic}
\IF{data value is between $b$ and $c$}
  \STATE{prob = 1.0}
\ELSIF{data value is between $a$ and $b$}
  \STATE{
    prob = $(\textrm{data}-a)/(b-a)$
  }
\ELSIF{data value is between $c$ and $d$}
  \STATE{
    prob = $(d-\textrm{data})/(d-c)$
  }
\ELSE \STATE{prob = 0.0}
\ENDIF
\end{algorithmic}

\begin{frame}
	\frametitle{Encoding of features and rules}
	\begin{itemize}
	\item The four parameters are encoded into blocks.
	\item Each block is a feature with values between 0.0 and 7.0.
	\end{itemize}

\begin{figure}
\begin{tabular}{|cccc|} \hline
010 & 011 & 100 & 101\\
a=2 & b=3 & c=4 & d=5\\
\hline\end{tabular}
\end{figure}

	\begin{itemize}
	\item A rule has 12 blocks of features, at the end is the type of attack.
	\end{itemize}

\begin{figure}
\begin{tabular}{|cccc|c|cccc|c|} \hline
010 & 011 & 100 & 101   & ...... & 010 & 011 & 101 & 111   & DoS\\
a=2 & b=3 & c=4 & d=5   & ...... & a=2 & b=3 & c=5 & d=7   &\\ 
    &     & Block 1&    &        &     & Block 12& &       & Type\\
\hline\end{tabular}
\end{figure}
